% import math notations
\input{notations.tex}

\usepackage[nopostdot,automake]{glossaries-extra}

\usepackage{ifthen}

\setabbreviationstyle{long-short}
\setglossarystyle{altlist}

\makeglossaries
% only show link on first use
\GlsXtrEnableEntryUnitCounting{general}{0}{chapter}
\renewcommand*{\glslinkcheckfirsthyperhook}{%
    \ifnum\glsentrycurrcount\glslabel>0
        \setkeys{glslink}{hyper=false}%
    \fi
}

% #1 - short name: OIL
% #2 - math symbol
% #3 - full name: Open Information Layer
% #4 - description

\newcommand{\newdualentry}[4]{%
    \ifthenelse{\equal{#2}{}}%
    {
        % If #2 (the math symbol) is empty
        \newglossaryentry{#1}{%
            name={#3 - #1},
            text={#1},
            short={#1},
            long={#3},
            first={#3 (#1)},
            firstplural={#3s (#1s)},
            description={#4},
            sort={#1}
        }
    }{
        % If #2 is provided
        \newglossaryentry{#1}{%
            name={#3 - \ensuremath{#2}},
            text={#1},
            short={\ensuremath{#2}},
            long={#3},
            first={#3 (\ensuremath{#2})},
            firstplural={#3s (#1s)},
            description={#4},
            symbol={\ensuremath{#2}},
            sort={#1}
        }
    }
}

\newdualentry{OW}{}{Open Web}{The next-generation Internet where information flows openly without any restrictions, as it is supposed to be.}

\newdualentry{OI}{}{Open Information}{Information that is typically found across various types of networks, including decentralized, federated, and centralized networks that allow permissionless access.}

\newdualentry{OIL}{}{Open Information Layer}{A decentralized and permissionless information layer where information flows openly without any restrictions.}

\newdualentry{DSL}{}{Data Sublayer}{A decentralized network where the Open Information flows from its source to its destination.}

\newdualentry{UMS}{}{Unified Metadata Schemas}{A unified set of data structures for interoperability.}

\newdualentry{SN}{\node}{Serving Node}{A Data Sublayer component that indexes, cleans, stores, and ultimately serves the Open Information to the end users. Denoted as \node\ when it is in Normal mode, and \publicGoodNode\ when it is in Public Good mode.}

\newdualentry{SNP}{\publicGoodNode}{Serving Node (Public Good Mode)}{A \gls{SN} that operates for the purpose of supporting Public Goods and strenthening the Network, it does not receive any \glsfmtlong{Fee} or \glsfmtlong{NR}.}

\newdualentry{RS}{\reliabilityScore}{Reliability Score}{A score used to determine the allocation of requests to \glsfmtlong{SN}s.}

\newdualentry{GI}{}{Global Indexer}{A \glsfmtlong{DSL} component that facilitates coordination among Serving Nodes and engages with the \glsfmtlong{VSL}.}

\newdualentry{VSL}{}{Value Sublayer}{A blockchain where the value created by Open Information activities is recorded and distributed.}

\newdualentry{PDS}{}{Permissionless Data Source}{A repository of data that can be accessed without the need for authorization or authentication.}

\newdualentry{NR}{\networkReward}{Network Rewards}{Tokens allocated by the RSS3 Network to incentivize network participants.}

\newdualentry{OR}{\operationReward}{Operation Rewards}{Tokens allocated to \glsfmtlong{OP} by the RSS3 Network to incentivize Node operation.}

\newdualentry{SR}{\stakingReward}{Staking Rewards}{Tokens allocated to \glsfmtlong{SP} by the RSS3 Network to incentivize network participation.}

\newdualentry{TR}{\trustReward}{Trust Rewards}{Tokens allocated to \glsfmtlong{PGP} by the RSS3 Network to incentivize network participation and support Nodes for Public Goods provision.}

\newdualentry{NO}{}{Node Operator}{An individual or organization that operates a Serving Node.}

\newdualentry{PGP}{\publicGoodPool}{Public Good Pool}{A collective pool of staked \$RSS3 that is used to improve the RSS3 Network by assigning trust to Public Good Nodes.}

\newdualentry{OP}{\operationPool}{Operation Pool}{A pool of \$RSS3 that consists of 1) Fees collected from serving Data Sublayer requests; 2) \glsfmtlong{NR} allocated based on the Node's work; 3) Tax collected from its Staking Pool.}

\newdualentry{SP}{\stakingPool}{Staking Pool}{A pool of staked \$RSS3 that is used to improve the RSS3 Network by assigning trust to Normal Nodes.}

\newdualentry{R3N}{}{RSS3 Network}{A decentralized network that is formed by a DSL and a VSL.}

\newdualentry{Epoch}{\epoch}{Epoch}{A period of time used as a reference to measure the \glsfmtlong{R3N}'s operation.}

\newdualentry{N}{\work}{number of requests served on the \glsfmtlong{DSL}}{The metric that reflects the Node's service and is used to determine the allocation of \glsfmtlong{NR} into a Node's \glsfmtlong{OP}.}

\newdualentry{Tax}{\tax}{Operation Tax}{A tax collected from the \glsfmtlong{NR} that are allocated to a Node's \glsfmtlong{SP}, by its \glsfmtlong{OP}.}

\newdualentry{Deposit}{\deposit}{Deposit}{Tokens required to operate a \glsfmtlong{SN}.}

\newdualentry{Fee}{\fee}{Request Fees}{Fees paid to \glspl{SN} for delivering \glsfmtlong{OI} from its \glsfmtlong{PDS} to the requesters.}

\newdualentry{Chip}{\chip}{Chip}{An ERC-721 Non-Fungible Tokens (NFTs) representing a network participant's stake in a particular Node.}

\newdualentry{Slashing}{}{Slashing}{A penalty imposed on a Node for misconduct.}

\newdualentry{REP}{}{RSS3 Evolution Proposal}{The proposal to change the RSS3 Network's parameters, processes and rules.}
