\section{Conclusion} 

% \red{We present the IPSA, a next-gen decentralized architecture designed for efficient information distribution. IPSA is orchestrated in the way that it has the potential to support virtually any information distribution-related use cases. }

We present the RSS3 Standard, a next-generation feed standard designed for information distribution. The standard enforces strong data ownership by including asset verification and on chain governance, and furthermore equips the feed with native support for interoperable interactions. The standard naturally enables flexible recommendation and searching implementation. We then propose the RSS3 Protocol that is fully conformed to the standard. In comparison to the original RSS, RSS3 is a refined and evolved protocol that supports complicated application scenarios.

To further illustrate the robustness of the standard, we demonstrate an RSS3 Network that implements multiple state-of-the-art measures to ensure data consistency and redundancy. This is achieved through: 1) a sophisticated network architecture that guarantees the network usability and stability; 2) a curated incentivization scheme that encourages all network participants to contribute toward the network's development. The orchestration has the potential to provide a truly decentralized network, that is, on top of all the benefits provided by existing solutions, with flexibility, efficiency, and extensibility.
\\
\\

\textbf{At the heart of Natural Selection Labs, we firmly believe in the freedom of information distribution: No organizations or authorities shall prohibit the free exercise of the right of people to create, store, and distribute their information.}