\subsection{Reward Pools}
\label{subsec:reward_pools}

The \glsfmtlong{R3N} allocates a portion of \$RSS3's total supply to incentivize network participants, referred to as the \glsfirst{NR},
and allocated into reward pools.

This section introduces three reward pools: the \glsfirst{OP}, the \glsfirst{SP}, and the \glsfirst{PGP}. See \Cref{fig:network-rewards} for an illustration.

\subsubsection{\glsfmtlong{OP} (\operationPool)}
\label{subsubsec:operation_pool}

An \glsfirst{OP} is used to store tokens that are allocated to a Normal Node from two sources:
\begin{enumerate}
    \item The \gls{Fee} collected from requests served on the \gls{DSL}
    \item The \gls{Tax} collected from the Node's \stakingPool
\end{enumerate}

The \glsfmtlong{NO} can set a tax rate, \taxRate, which is applied to its \stakingPool, in conjunction with its \gls{Deposit} to determine the amount of \gls{Tax} collected from its \stakingPool.
See \Cref{subsubsec:taxation}.
The tax applies to the \glsfmtlong{NR} allocated to the Node's \stakingPool, not the staked tokens.

Only the corresponding \glsfmtlong{NO} can withdraw tokens from its \operationPool, and the withdrawal is subject to a waiting period imposed by the Network.

\subsubsection{\glsfmtlong{SP} (\stakingPool)}
\label{subsubsec:staking_pool}

A \glsfirst{SP} is used to store staked tokens for a Normal Node. Network participants can stake tokens into a Normal Node's \stakingPool\ to increase the Node's chance to receive requests on the \gls{DSL}.

The allocation of \glsfmtlong{NR} into a Node's \stakingPool\ at the end of each epoch \epoch, is determined by two factors:
\begin{enumerate}
    \item \gls{OR}, the Node's normalized work contribution \work\ in proportion to the total work done on the \gls{DSL} (See \Cref{subsubsec:staking_rewards})
    \item \gls{SR}, the Node's \stakingPool\ size in proportion to the total staked tokens on the \gls{VSL} (See \Cref{subsubsec:operation_rewards})
\end{enumerate}

A tax \tax\ set by its \glsfmtlong{NO} is then applied to the received Rewards.

\subsubsection{\glsfmtlong{PGP} (\publicGoodPool)}

As Public Good Nodes do not participate in incentivization, they collectively share a \glsfirst{PGP} for network participants to show their support towards Public Goods provision.

This pool plays a crucial role in facilitating the provision of Public Goods and reinforcing the robustness of the Network.
The pool has a unique \tax\ set by the Network, and the proceeds are donated to initiatives and clauses that are oriented towards Public Good.
